%! TeX root = cv.tex
\documentclass[10pt]{article}       % set main text size
\usepackage[a4paper,                % set paper size to A4. change to letterpaper for US/Canadian resumes
top=0.4in,                          % specify top page margin
bottom=0.4in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin

\usepackage{helvet}                 % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt}

\begin{document}

\centerline{\Huge Joan Dot Sastre}

\vspace{5pt}

\centerline{\href{mailto:joandot1998@gmail.com}{joandot1998@gmail.com} | \href{https://github.com/DinDotDout}{github.com/DinDotDout}}

\vspace{-10pt}
\section*{Summary}
% A committed graphics programmer with 2 years of professional experience and 5 years dedicated to mastering the craft. Skilled in shader programming, performance optimization, and 3D graphics. Eager to deepen my knowledge of lower-level APIs and contribute to innovative and visually stunning games. Passionate about open-source projects and refining my workflow.
A committed graphics programmer with 2 years of professional experience and 5 years dedicated to mastering the craft, having worked on the game "Continuum World" and another unreleased project. Skilled in shader programming, performance optimization, and 3D graphics. Eager to deepen my knowledge of lower-level APIs and contribute to innovative and visually stunning games. Passionate about open-source projects and refining my workflow.
\section*{Skills}
\textbf{Engines} Godot, Unity \\
\textbf{Coding} C++, C\#, GDScript, GLSL, Lua, Python \\
\textbf{Tools} Renderdoc, DAP, Git, CMake \\
\textbf{Low level APIs} Vulkan \\
\textbf{Languages} Spanish (native), Catalan (native), English (Cambridge C2 Proficiency)

\vspace{-6.5pt}

\section*{Experience}
\textbf{Generalist/Graphics Programmer ,} {Game Motion} \hfill 2022 -- 2023\\
\vspace{-9pt}
\begin{itemize}
	\item Developed a system for a 2.5D top-down game that constructs 2D procedural meshes. These
	      are then processed by a shader which applies color, places decals, and transforms them based on view
	      to simulate a 3D appearance
	\item Boosted performance of farthest LODs from an average of 26 fps to 60 fps using instanced rendering
	\item Created a system allowing screen space targeted shader effects through a mask buffer
	\item Developed shaders for elements including river water, different biome grounds, cloud backgrounds and game VFX
	\item Devised a tool for artists to create animated and cohesive prop variations using sprite
	      selection, spatial transforms, and color shift constraints. It offers instant previews
	      for any changes, allowing for a rapid creation workflow
	\item Developed a 2.5D parallax system using multiple billboartd sprite layers, which adjust their position and apparent distance based on camera tilt, zoom, rotation, and position
\end{itemize}

\textbf{Junior Generalist Programmer,}  {Ninju Games} \hfill 2021 -- 2022 \\
\vspace{-9pt}
\begin{itemize}
	\item Worked on an unreleased project multiplayer implementation and port to Nintendo Switch
	\item Built 2D procedural map generation tools with shape, biome distributions, river placement parameters
	\item Created a system for prop placement and destruction, enabling world refill and spatial distribution according to GDD
	\item Implemented a multi-threaded asset manager for tracking, loading and fetching from both local and remote sources
\end{itemize}

\vspace{-18.5pt}

\section*{Personal Projects}
% \textbf{Dot Renderer} \hfill\\
% Unreleased vulkan based renderer to test 
\textbf{Marching Cloudscapes} \hfill \href{https://github.com/DinDotDout/marching_cloudscapes}{github.com/DinDotDout/marching\_cloudscapes} \\
% Developed a raymarcher shader for a skybox, which incorporated physically
% based volumetric clouds, flat high altitude clouds, and simulated atmospheric scattering. My
% research and testing of various optimization techniques resulted in a consistent 144fps given
% optimal parameters. The project also provided a broad range of customizable parameters and
% settings to simulate various cloud types. I added artist drawable cloudscape maps for scenery
% building and explored various noise functions and their combinations for generating realistic cloud shapes.

Developed a raymarcher shader for a skybox, incorporating volumetric clouds, 2D high altitude clouds,
and atmospheric scattering. Optimized to achieve a consistent draw time of 7 to 8 ms per frame. Provided customizable
parameters for various cloud types and added drawable cloudscape maps for scenery building.

% \vspace{-9pt}
% \begin{itemize}
% \item Developed a raymarcher shader for a skybox, incorporating physically based volumetric clouds, flat high altitude clouds and simulated atmospheric scattering
% \item Researched and tested many optimization techniques, achieving a consistent 144fps given optimal parameters
% \item Provided a broad range of customizable parameters and settings to simulate various cloud types
% \item Added artist drawable cloudscape maps for scenary building
% \item Explored various noise functions and their combinations for generating realistic cloud shapes
% \end{itemize}

\vspace{5pt}
\textbf{Godot Texture Composer} \hfill \href{https://github.com/DinDotDout/noise_texture_composer}{github.com/DinDotDout/noise\_texture\_composer} \\
Developed a tool to combine single-channel Godot noise or gradient textures into a multi-channel
texture, reducing shader texture lookups and significantly optimizing shader performance.
% Encountered a situation where shader performance in Godot was being hindered due to multiple
% texture lookups, as the inbuilt texture creation utilities were using only one channel. In
% response, I created a tool that combined single-channel Godot noise or gradient textures into a
% multi-channel texture. This resulted in single shader texture lookup, significantly optimizing shader performance

% \textbf{Neural Network for Tetris99 on Nintendo Switch} \hfill \href{https://github.com/DinDotDout/tfg_tetrisIA }{github.com/DinDotDout/tfg\_tetrisIA} \\
% \vspace{-9pt}
% \begin{itemize}
% 	\item Developed a reduced replica of Tetris99 for training a neural network
% 	\item Implemented real time image processing techniques for game state extraction and noise filtering
% 	\item Used Arduino for console input, enabling the machine learning model to interact with the game environment
% 	\item Trained a neural network to play the game, achieving an average of 0.467 lines cleared per second on the console
% \end{iTemize}

\vspace{5pt}
\textbf{Apprentice Binder} \hfill \href{https://github.com/andriybyelikov/apprentice-binder}{github.com/andriybyelikov/apprentice-binder} \\
Short 2.5D physics-based puzzle platformer card game where you use a hand of cards dealt to you to
summon creatures that help you overcome obstacles and reach the end of a set of levels.

\vspace{5pt}
\textbf{DOT (Procedural Planet Game/Editor)} \hfill \href{https://github.com/DinDotDout/dot}{github.com/DinDotDout/dot} \\
An interactive game featuring customizable procedural planet generation with randomized prop
and enemy spawn. It includes four distinct biomes, variable planet sizes, and seed control.
The game offers three distinct modes: tower defense, third-person sword combat, and space-ship flight and shoot.
% \vspace{-9pt}
% \begin{itemize}
% 	\item Built interactive, non-blocking procedural planet generation in the menu
% 	\item Implemented height based shader texturing on the planet
% 	\item Added randomized non colliding prop spawn
% 	\item Created three game modes: tower defense, third person sword combat and space-ship flight and shoot
% \end{itemize}
\vspace{5pt}
\vspace{-18.5pt}
\section*{Education}
\textbf{\href{https://www.uib.eu/}{UIB}} -- Bachelor's Degree in Computer Science \hfill 2021 \\

\end{document}

